Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology

### 2019-05-23 reproducing_registered_reports.Rmd
preprint

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article. @hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal *Cognition*. Eleven  articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. Hardwicke et al. (2018) estimated that it took between 2-4 hours to reproduce the reported results, but they did not record the exact time. @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one could not be reproduced due to a lack of a software license, and 16 articles could not be reproduced with access to the required software. For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. @stodden_empirical_2018 analyzed data availability in the journal *Science* in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26% was estimated to be computationally reproducible. These studies reveal that there is clear room for improvement in how reproducible published articles are.

@@

To find Registered Reports published in psychology we drew from a database of registered reports maintained by by Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018]. Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left `r length(all_data$doi)` studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional studies.

@@

\begin{figure*}
\begin{center}
\includegraphics{fig1.png}

@@

One of the reasons to share data is allow other researchers to reproduce the reported results. Another important reason to share data is to enable other researchers to reuse the data. If the data can be understood by others, they can be used to answer novel research questions. This is one of the reasons why it is recommended to describe the dataset variables in a codebook. If the variables are not clearly described (e.g., the dataset consists of variables identified by abbreviations that only make sense to the original researcher), other researchers will not be able to reuse the data to answer novel questions. In our analyses, data were scored as 'understandable' when all variables were clearly named (e.g., 'Condition') and the values for variables were labeled (e.g., 0 = control, 1 = experimental). Out of the `r sum(all_data$not_software_specific, na.rm = TRUE)` papers with available data in a format that was not software specific, only `r sum(all_data$understandable, na.rm = TRUE)` datasets were described in enough detail to be understandable. This highlights the importance of adding a codebook with a datafile. For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see @arslan_how_2019.

@@

There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG and NC had more experience). The more expertise coders had, the easier it was to reproduce findings (which lead to lower inter-rater reliability). This raises the question regarding which level of skill is expected to be able to reproduce results reported in a scientific article. The required experience might be difficult to quantify. Our results concerning the reproducibility of results is based on which results a PhD student with experience in the statistical software and educated in the same scientific discipline could reproduce, which we feel is a reasonable standard. For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results.

All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g. overlooked script files). The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve). It should be noted that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.

@@

Nevertheless, the reproducibility rate for articles where data and code were available show there is clear room for improvement in how reproducible published Registered Reports are, when we attempted to reproduce main analyses without contacting the authors. One of the main goals of our project was to identify ways to improve the reproducibility of published articles. We encountered several common issues that made results reported in Registered Reports difficult to reproduce (cf. Hardwicke et al., 2018). This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output anaysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process. We will discuss each of these points below, and link to examples of good practices that we encountered.

@@

In addition to the recommendations we have provided above, we believe novel technological solutions might improve the reproducibility of research articles. For example, CodeOcean is an online, cloud based, computational reproducibility platform [@clyburne-sherin_computational_2018]. It provides a code environment (or container) that runs online, which means that researchers using CodeOcean do not have to download data, code, or software, but can analyze the data in their browser. It is not yet possible to use SPSS within CodeOcean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations. Another solution is RMarkdown which enable researchers to write fully reproducible manuscripts. RMarkdown files load the raw data and allow researchers to compute each number reported in the manuscript from the data, instead of copy-pasting values. This means that, as long as the data and require packages can be loaded, all reported numbers can be reproduced. This saves a lot of time matching the analysis code to the reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced by the code. The current manuscript is an example of a reproducible RMarkdown file.^[see https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd] Additional solutions that help researchers to share reproducible analyses might become available in the future.

>>>>

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article. @hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal *Cognition*. Eleven  articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. Hardwicke et al. (2018) estimated that it took between 2-25 hours to reproduce the reported results, but they did not record the exact time. @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one could not be reproduced due to a lack of a software license, and 16 articles could not be reproduced with access to the required software. For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. @stodden_empirical_2018 analyzed data availability in the journal *Science* in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26% was estimated to be computationally reproducible. These studies reveal that there is clear room for improvement in how reproducible published articles are.

@@

To find Registered Reports published in psychology we drew from a database of registered reports maintained by the Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018]. Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left `r length(all_data$doi)` studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional studies.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{fig1.png}

@@

One of the reasons to share data is to allow other researchers to reproduce the reported results. Another important reason to share data is to enable other researchers to reuse the data. If the data can be understood by others, they can be used to answer novel research questions. This is one of the reasons why it is recommended to describe the dataset variables in a codebook. If the variables are not clearly described (e.g., the dataset consists of variables identified by abbreviations that only make sense to the original researcher), other researchers will not be able to reuse the data to answer novel questions. In our analyses, data were scored as 'understandable' when all variables were clearly named (e.g., 'Condition') and the values for variables were labeled (e.g., 0 = control, 1 = experimental). Out of the `r sum(all_data$not_software_specific, na.rm = TRUE)` papers with available data in a format that was not software specific, only `r sum(all_data$understandable, na.rm = TRUE)` datasets were described in enough detail to be understandable. This highlights the importance of adding a codebook with a datafile. For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see @arslan_how_2019.

@@

There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG and NC had more experience). The more expertise coders had, the easier it was to reproduce findings (which lead to lower inter-rater reliability). This raises the question regarding which level of skill is expected to be able to reproduce results reported in a scientific article. The required experience might be difficult to quantify. Our results concerning the reproducibility of results is based on which results a PhD student with experience in the statistical software and educated in the same scientific discipline could reproduce, which we feel is a reasonable standard. For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results. All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g. overlooked script files). The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve). It should be noted that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.

@@

Nevertheless, the reproducibility rate for articles where data and code were available show there is clear room for improvement in how reproducible published Registered Reports are, when we attempted to reproduce main analyses without contacting the authors. One of the main goals of our project was to identify ways to improve the reproducibility of published articles. We encountered several common issues that made results reported in Registered Reports difficult to reproduce (cf. Hardwicke et al., 2018). This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output analysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process. We will discuss each of these points below, and link to examples of good practices that we encountered.

@@

In addition to the recommendations we have provided above, we believe novel technological solutions might improve the reproducibility of research articles. For example, Code Ocean is an online, cloud based, computational reproducibility platform [@clyburne-sherin_computational_2018]. It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser. It is not yet possible to use SPSS within Code Ocean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.^[For a Code Ocean capsule reproducing this manuscript: https://codeocean.com/capsule/8580632/tree/v1] Another solution is RMarkdown which enable researchers to write fully reproducible manuscripts. RMarkdown files load the raw data and allow researchers to compute each number reported in the manuscript from the data, instead of copy-pasting values. This means that, as long as the data and require packages can be loaded, all reported numbers can be reproduced. This saves a lot of time matching the analysis code to the reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced by the code. The current manuscript is an example of a reproducible RMarkdown file.^[See https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd] Additional solutions that help researchers to share reproducible analyses might become available in the future.

### 2019-05-23 reproducing_registered_reports.tex
preprint

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article. Hardwicke et al. (2018) examined the reproducibility of 35 articles published in the journal \emph{Cognition}. Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. Hardwicke et al.~(2018) estimated that it took between 2-4 hours to reproduce the reported results, but they did not record the exact time. Stockemer, Koehler, and Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one could not be reproduced due to a lack of a software license, and 16 articles could not be reproduced with access to the required software. For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. Stodden, Seiler, and Ma (2018) analyzed data availability in the journal \emph{Science} in 2011-2012 and found that 26 of 204 (or 13\%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26\% was estimated to be computationally reproducible. These studies reveal that there is clear room for improvement in how reproducible published articles are.

@@

To find Registered Reports published in psychology we drew from a database of registered reports maintained by by Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports (Hagger et al., 2016) and Many Labs projects (Klein et al., 2014, 2018). Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left 62 studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of 5 additional studies.

@@

One of the reasons to share data is allow other researchers to reproduce the reported results. Another important reason to share data is to enable other researchers to reuse the data. If the data can be understood by others, they can be used to answer novel research questions. This is one of the reasons why it is recommended to describe the dataset variables in a codebook. If the variables are not clearly described (e.g., the dataset consists of variables identified by abbreviations that only make sense to the original researcher), other researchers will not be able to reuse the data to answer novel questions. In our analyses, data were scored as \enquote{understandable} when all variables were clearly named (e.g., \enquote{Condition}) and the values for variables were labeled (e.g., 0 = control, 1 = experimental). Out of the 42 papers with available data in a format that was not software specific, only 21 datasets were described in enough detail to be understandable. This highlights the importance of adding a codebook with a datafile. For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see Arslan (2019).

@@

There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG and NC had more experience). The more expertise coders had, the easier it was to reproduce findings (which lead to lower inter-rater reliability). This raises the question regarding which level of skill is expected to be able to reproduce results reported in a scientific article. The required experience might be difficult to quantify. Our results concerning the reproducibility of results is based on which results a PhD student with experience in the statistical software and educated in the same scientific discipline could reproduce, which we feel is a reasonable standard. For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results.

All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.~overlooked script files). The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve). It should be noted that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.

@@

Nevertheless, the reproducibility rate for articles where data and code were available show there is clear room for improvement in how reproducible published Registered Reports are, when we attempted to reproduce main analyses without contacting the authors. One of the main goals of our project was to identify ways to improve the reproducibility of published articles. We encountered several common issues that made results reported in Registered Reports difficult to reproduce (cf.~Hardwicke et al., 2018). This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output anaysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process. We will discuss each of these points below, and link to examples of good practices that we encountered.

@@

In addition to the recommendations we have provided above, we believe novel technological solutions might improve the reproducibility of research articles. For example, CodeOcean is an online, cloud based, computational reproducibility platform (Clyburne-Sherin, Fei, \& Green, 2018). It provides a code environment (or container) that runs online, which means that researchers using CodeOcean do not have to download data, code, or software, but can analyze the data in their browser. It is not yet possible to use SPSS within CodeOcean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations. Another solution is RMarkdown which enable researchers to write fully reproducible manuscripts. RMarkdown files load the raw data and allow researchers to compute each number reported in the manuscript from the data, instead of copy-pasting values. This means that, as long as the data and require packages can be loaded, all reported numbers can be reproduced. This saves a lot of time matching the analysis code to the reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced by the code. The current manuscript is an example of a reproducible RMarkdown file.\footnote{see \url{https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd}} Additional solutions that help researchers to share reproducible analyses might become available in the future.

>>>>

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article. Hardwicke et al. (2018) examined the reproducibility of 35 articles published in the journal \emph{Cognition}. Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. Hardwicke et al.~(2018) estimated that it took between 2-25 hours to reproduce the reported results, but they did not record the exact time. Stockemer, Koehler, and Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one could not be reproduced due to a lack of a software license, and 16 articles could not be reproduced with access to the required software. For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. Stodden, Seiler, and Ma (2018) analyzed data availability in the journal \emph{Science} in 2011-2012 and found that 26 of 204 (or 13\%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26\% was estimated to be computationally reproducible. These studies reveal that there is clear room for improvement in how reproducible published articles are.

@@

To find Registered Reports published in psychology we drew from a database of registered reports maintained by the Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports (Hagger et al., 2016) and Many Labs projects (Klein et al., 2014, 2018). Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left 62 studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software, Python, Matlab), which led to the exclusion of 5 additional studies.

@@

One of the reasons to share data is to allow other researchers to reproduce the reported results. Another important reason to share data is to enable other researchers to reuse the data. If the data can be understood by others, they can be used to answer novel research questions. This is one of the reasons why it is recommended to describe the dataset variables in a codebook. If the variables are not clearly described (e.g., the dataset consists of variables identified by abbreviations that only make sense to the original researcher), other researchers will not be able to reuse the data to answer novel questions. In our analyses, data were scored as \enquote{understandable} when all variables were clearly named (e.g., \enquote{Condition}) and the values for variables were labeled (e.g., 0 = control, 1 = experimental). Out of the 42 papers with available data in a format that was not software specific, only 21 datasets were described in enough detail to be understandable. This highlights the importance of adding a codebook with a datafile. For an explanation of how to create machine-readable codebooks (which was also used to create the codebook that is part of this manuscript) see Arslan (2019).

@@

There were differences between coders in how much expertise they had with R, SPSS, and JASP (PO had less experience, while JG and NC had more experience). The more expertise coders had, the easier it was to reproduce findings (which lead to lower inter-rater reliability). This raises the question regarding which level of skill is expected to be able to reproduce results reported in a scientific article. The required experience might be difficult to quantify. Our results concerning the reproducibility of results is based on which results a PhD student with experience in the statistical software and educated in the same scientific discipline could reproduce, which we feel is a reasonable standard. For the current analysis, we considered a study reproducible as long as the more experienced coder could reproduce the main results. All authors have collectively discussed disagreements, which on several occasions led to clarifying ambiguities in rating strategies and correcting mistakes in the process of paper analysis (e.g.~overlooked script files). The final ratings presented here have been discussed and approved by all authors, but will not be completely flawless, and we expect different teams of coders to reach slightly different conclusions (i.e., perfect reliability would be extremely difficult to achieve). It should be noted that the main goal of our analysis is to evaluate where there is room for improvement, and identify practices that researchers can use to make there work more reproducible.

@@

Nevertheless, the reproducibility rate for articles where data and code were available show there is clear room for improvement in how reproducible published Registered Reports are, when we attempted to reproduce main analyses without contacting the authors. One of the main goals of our project was to identify ways to improve the reproducibility of published articles. We encountered several common issues that made results reported in Registered Reports difficult to reproduce (cf.~Hardwicke et al., 2018). This leads to 4 points researchers in psychology should focus on to improve reproducibility, namely (a) add a codebook to data files, (b) annotate code so it is clear what the code does, and clearly structure code (e.g., using a README) so others know which output analysis code creates, (c) list packages that are required in R and the versions used at the top of your R file, (d) check whether the code you shared still reproduces all analyses after revisions during the peer review process. We will discuss each of these points below, and link to examples of good practices that we encountered.

@@

In addition to the recommendations we have provided above, we believe novel technological solutions might improve the reproducibility of research articles. For example, Code Ocean is an online, cloud based, computational reproducibility platform (Clyburne-Sherin, Fei, \& Green, 2018). It provides a code environment (or container) that runs online, which means that researchers using Code Ocean do not have to download data, code, or software, but can analyze the data in their browser. It is not yet possible to use SPSS within Code Ocean, but for R code it solves the problem of package versions (since the container uses the version of packages specified by the researchers) and file locations.\footnote{For a Code Ocean capsule reproducing this manuscript: \url{https://codeocean.com/capsule/8580632/tree/v1}} Another solution is RMarkdown which enable researchers to write fully reproducible manuscripts. RMarkdown files load the raw data and allow researchers to compute each number reported in the manuscript from the data, instead of copy-pasting values. This means that, as long as the data and require packages can be loaded, all reported numbers can be reproduced. This saves a lot of time matching the analysis code to the reported results, and thus speeds up the process of checking whether all results reported in the manuscripts are reproduced by the code. The current manuscript is an example of a reproducible RMarkdown file.\footnote{See \url{https://github.com/Lakens/reproducing_registered_reports/blob/master/reproducing_registered_reports.Rmd}} Additional solutions that help researchers to share reproducible analyses might become available in the future.
